---
title: "Training Week of 4/27"
output:
  word_document: default
  html_document: default
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```



# Monday 

Plan for 60 minutes of easy running. No looking at watch. Should run with Rowan. 

### Miles Run and Average Pace 

```{r}
library(hms)
miles_run1= 8.57
print(miles_run1)
time_running1=hms(0,60)
converted_time_running=as.numeric(time_running1)
dec_runningtime=converted_time_running/miles_run1
time_in_minutes=(dec_runningtime)/60
floored_minutes=floor(time_in_minutes)
dec=time_in_minutes-trunc(time_in_minutes)
time_in_seconds=dec*60
time_stored=(hms(time_in_seconds,floored_minutes))
print(time_stored)
```

# Tuesday 

Plan for 70 minutes of easy running. No looking at watch. Goal of 10 miles, but less is A-okay. 


### Projected Miles Run and Average Pace 

```{r}
miles_run2=10
print(miles_run2)
time_running2=hms(0,10,1)
converted_time_running=as.numeric(time_running2)
dec_runningtime=converted_time_running/miles_run2
time_in_minutes=(dec_runningtime)/60
floored_minutes=floor(time_in_minutes)
dec=time_in_minutes-trunc(time_in_minutes)
time_in_seconds=dec*60
time_stored=(hms(time_in_seconds,floored_minutes))
print(time_stored)
```


# Wednesday 

Plan for 85 minutes of easy running.   

### Projected Miles Run and Average Pace 
```{r}
miles_run3=12
print(miles_run3)
time_running3=hms(00,24,1)
converted_time_running=as.numeric(time_running3)
dec_runningtime=converted_time_running/miles_run3
time_in_minutes=(dec_runningtime)/60
floored_minutes=floor(time_in_minutes)
dec=time_in_minutes-trunc(time_in_minutes)
time_in_seconds=dec*60
time_stored=(hms(time_in_seconds,floored_minutes))
print(time_stored)
```


# Thursday 

70 minutes of easy running. 8*45/15 at Johnson's rock in the middle, with 6x hills after. 

### Projected Miles Run and Average Pace 
```{r}
miles_run4=10
print(miles_run4)
time_running4=hms(00,10,1)
converted_time_running=as.numeric(time_running4)
dec_runningtime=converted_time_running/miles_run4
time_in_minutes=(dec_runningtime)/60
floored_minutes=floor(time_in_minutes)
dec=time_in_minutes-trunc(time_in_minutes)
time_in_seconds=dec*60
time_stored=(hms(time_in_seconds,floored_minutes))
print(time_stored)
```


# Friday 

70 minutes of easy running. 4x30 seconds on, 30 seconds off, at harder effort in the middle, or whenever there is some flat ground. 

### Projected Miles Run and Average Pace 
```{r}
miles_run5=10
print(miles_run5)
time_running5=hms(00,10,1)
converted_time_running=as.numeric(time_running5)
dec_runningtime=converted_time_running/miles_run5
time_in_minutes=(dec_runningtime)/60
floored_minutes=floor(time_in_minutes)
dec=time_in_minutes-trunc(time_in_minutes)
time_in_seconds=dec*60
time_stored=(hms(time_in_seconds,floored_minutes))
print(time_stored)
```  
# Saturday 

10 day after the last workout, so it's time to give the body a little hit again. Plan for 6 mile tempo at 5:20 pace at Johnson's rock. Total time: 32 minutes. The body should be able to handle this following last week's 8*3 on, 1 off fartlek. Let's get it. 

15 minute warmup, workout in 32 minutes, and 20 minute cooldown. 

### Projected Miles Run and Average Pace 
```{r}
miles_run6=10.6
print(miles_run6)
time_running6=hms(00,7,1)
converted_time_running=as.numeric(time_running6)
dec_runningtime=converted_time_running/miles_run6
time_in_minutes=(dec_runningtime)/60
floored_minutes=floor(time_in_minutes)
dec=time_in_minutes-trunc(time_in_minutes)
time_in_seconds=dec*60
time_stored=(hms(time_in_seconds,floored_minutes))
print(time_stored)
```




# Sunday 

Easy long run. 16 miles in 1:50 or so. Keep the aerobic stimulus up, but in a smart way. 

### Projected Miles Run and Average Pace 
```{r}
miles_run7=16
print(miles_run7)
time_running7=hms(0,52,1)
converted_time_running=as.numeric(time_running7)
dec_runningtime=converted_time_running/miles_run7
time_in_minutes=(dec_runningtime)/60
floored_minutes=floor(time_in_minutes)
dec=time_in_minutes-trunc(time_in_minutes)
time_in_seconds=dec*60
time_stored=(hms(time_in_seconds,floored_minutes))
print(time_stored)
```




# Total Miles for the Week 


```{r}
miles_total=data.frame(miles_run1, miles_run2,miles_run3,miles_run4, miles_run5,miles_run6,miles_run7)
new_variable=sum((miles_total))
print(new_variable)
```

# Total Time for the Week 
```{r}
hours_run=as.numeric(time_running1+time_running2+time_running3+time_running4+time_running5+time_running6+time_running7)
converted_hours=hours_run/3600
floored_hours=floor(converted_hours)
converted_minutes=converted_hours-trunc(converted_hours)
dec_minutes=converted_minutes*60
print(hms(0,dec_minutes,floored_hours))
```

# Average Pace for the Week 

```{r}
#need to get the total miles run for the week 
miles_total=data.frame(miles_run1, miles_run2,miles_run3,miles_run4, miles_run5,miles_run6,miles_run7)
total_miles=sum((miles_total))

#need to get the total minutes for the week 
hours_run=as.numeric(time_running1+time_running2+time_running3+time_running4+time_running5+time_running6+time_running7)
into_minutes=hours_run/60

#need to divide the total minutes for the week by the total miles for the week 

minutes_per_mile=into_minutes/total_miles

#need to floor the minutes and seconds 

floored_minutes_total=floor(minutes_per_mile)
dec=minutes_per_mile-trunc(minutes_per_mile)
time_in_seconds=dec*60
time_stored=(hms(time_in_seconds,floored_minutes_total))

print(time_stored)
```




